Gaps in stellar streams as a result of globular cluster fly-bys

### 2025-01-27 paper/main.tex
added point about incomplete census and evaporation of population

  Future work should involve a systematic comparison of gap creation rates across various Galactic potentials and extend the scope to a wider range of streams and globular clusters. This would help identify regimes where baryonic and dark matter-induced substructures can be disentangled, shedding light on the elusive influence of dark matter sub-halos on stellar streams. Additionally, we can continue to add realistic physics to the Galactic environment such as the merger of the Sagittarius dwarf galaxy and the passages of the Large and Small Magellanic clouds.

>>>>

  Future work should involve a systematic comparison of gap creation rates across various Galactic potentials and extend the scope to a wider range of streams and globular clusters. This would help identify regimes where baryonic and dark matter-induced substructures can be disentangled, shedding light on the elusive influence of dark matter sub-halos on stellar streams. Additionally, we can continue to add realistic physics to the Galactic environment such as: the merger of the Sagittarius dwarf galaxy, the passages of the Large and Small Magellanic clouds, as well as a time evolving globular cluster population that compensates for the clusters' mass loss, evaporation, and similarly add members from the current incomplete census.
